---
title: "googleplaydataset"
author: "Chen Ning Kuan"
date: "2020年1月27日"
output: 
  html_document:
    theme: cerulean
    toc: true
    # toc_depth: 2
    number_sections: true
  # word_document
---

## 論文ANdroid tobit model

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(dplyr)
require(magrittr)
library(readr)
require(ggplot2)
require(stringr)
options(scipen = 9)
library(tidyverse)
require(DT)
require(ranger)
require(GGally)
require(AER)
library(data.table) ##載入
library(stringr)
require(ranger)
library(stargazer)
require(rminer)
library(text2vec)
require(e1071)
library(C50)
library(pROC) 
library(data.table)
library(text2vec)
library(glmnet)
require(caret)
require(jiebaR)
require(MASS)
require(stargazer)
```

# 1.變數介紹:

我們有13個變數，包含10841個樣本

- App:Application name

- Category:Category the app belongs to

- Rating:Overall user rating of the app (as when scraped)

- Reviews:Number of user reviews for the app (as when scraped)

- Size:Size of the app (as when scraped)

- Installs:Number of user downloads/installs for the app (as when scraped)

- Type:Paid or Free

- Price:Price of the app (as when scraped)

- Content Rating:Age group the app is targeted at - Children / Mature 21+ / Adult

- Genres:An app can belong to multiple genres (apart from its main category). For eg, a musical family game will belong to Music, Game, Family genres.

- Last UpdatedDate: when the app was last updated on Play Store (as when scraped)

- Current VerCurrent: version of the app available on Play Store (as when scraped)

- Android Ver:Min required Android version (as when scraped)



# 2.資料處理方式

## 2.1刪掉的變數

我們刪掉 App,Last UpdatedDate,Current VerCurrent,Android Ver這4個變數

## 2.2變數處理方式

- 將Size變數全部轉成MB大小，並且刪除Size變數中 大小隨裝置改變的APP樣本去除
- 將Installs變數的"+"號去除
- 將Rating變數NA的樣本去除
- 新增一個變數叫做small app ，容量小於1MB的叫做small app

最後剩下7729個樣本和10個變數

```{r     include=FALSE  }
getwd()
data<- read_csv("googleplaystore.csv")
datause <- data
#datause<- data.table(datause)

review<- read_csv("googleplaystore_user_reviews.csv")
```

```{r    include=FALSE   }

datause <- datause[-which(datause$Rating>5),]
#datause 
#datause<- datatable( datause  )

datause$Price <- as.numeric(gsub('[$]', '', datause$Price))
datause$Price<- as.numeric(datause$Price)

datause$Installs <- as.numeric(gsub('[+,]', '', datause$Installs))

sum(is.na(datause$Rating))

```

```{r     include=FALSE            }

class(datause$Size)
#datause$Size <- factor( datause$Size  )
#levels(datause$Size)

#datause$Size<- as.character(datause$Size)

datause2 <- datause[-which(datause$Size=="Varies with device" ),]#以下刪掉 大小隨裝置改變的樣本

datause2$size <- str_sub(datause2$Size, end=-2)

```

```{r       include=FALSE}
right = function(x,n){
  substring(x,nchar(x)-n+1)
}
```

```{r     include=FALSE       }
#right(datause2$Size,1 )
datause2$mk <-right(datause2$Size,1 ) 
datause2$size <- as.numeric(datause2$size)
datause2$size_mb <- ifelse(datause2$mk=="k",1/1024,1)*datause2$size
datause2$small_app <-ifelse(datause2$mk=="k",1,0)
datause2 <- datause2[ ,-5]
datause2 <- datause2[,-14]
datause2 <- datause2[,-13]
datause2 <- datause2[,-c(1,10,11,12)]
dim(datause2)
datause2<- datause2[-which(is.na(datause2$Rating)),]
sum(is.na.data.frame(
datause2)) #check any NA in data.frame
```

```{r   include=FALSE       }
datause2$`Content Rating`<- factor(datause2$`Content Rating`)
levels(datause2$`Content Rating`  )
datause2$Type<- factor(datause2$Type)
datause2$Category<- factor(datause2$Category)
datause2$Genres<- factor(datause2$Genres)
#levels(datause2$Genres)
#levels(datause2$Category)


datause2<- 
datause2 %>% rename(Content_Rating=`Content Rating`)

```

show the summary statistic in r

```{r}

datause3 <- as.data.frame(datause2)
#stargazer(datause3,omit.summary.stat = c("p25", "p75"))

```


```{r}
df <- datause3[,-c(1,5,7,8)]
correlation.matrix <- cor(df) 

#stargazer(correlation.matrix, title = "Android APP的相關係數矩陣")

M<- cor(df)
library(corrplot)
corrplot(M, method="number")

```


# 3.感興趣的問題

```{r}
qplot(Rating, data = datause3, geom = "density",
  fill = Type, alpha = I(.5),
  main="Distribution of App rating",
  xlab="Rating",
  ylab="Density")
```



## 3.1哪些因素會影響APP的訂價

  這裡我們配適Tobit model中的corner soution 模型，以Price作為outcome，以Review,Rating,Installs,size_mb,small_app作為feature 
，這裡使用Tobit model是因為Price有很多價格都等於0

  note: 這裡我是參考別人配適婚外情的data，我不太確定left cersored在0是不是就等價
Tobit model中的corner soution


```{r}
fm.tobit <- tobit(Price ~Reviews,
data = datause2)
m1 <- summary(fm.tobit)

fm.tobit <- tobit(Price ~Reviews+Rating,
data = datause2)

m2 <- summary(fm.tobit)
fm.tobit <- tobit(Price ~Reviews+Rating+Installs,
data = datause2)
m3 <- summary(fm.tobit)
fm.tobit <- tobit(Price ~Reviews+Rating+Installs+size_mb,
data = datause2)
m4 <- summary(fm.tobit)

fm.tobit <- tobit(Price ~Reviews+Rating+Installs+size_mb+small_app,
data = datause2)
m5 <- summary(fm.tobit)
```


```{r}
m1
m2
m3
m4
m5
```


low(1-10000)

medium(10000-1000000)

high(10^6 up)

```{r}

#ifelse(datause2$Installs<10000 ,"low" ,"medium"     ) 
a<- datause2$Installs

ordinal<- cut(a, c(-Inf,10000,1000000,Inf), c("low","medium","high"),right=T)

datause2$ordinal <- ordinal

df <- datause2[,-c( 1,4,8  )]
#a[which(1000000<=a),1] <- "high"
#a[which(a<10000),1]<-"low"
#a[which(10000<=a&a<1000000),1] <- "medium"

m <- polr(ordinal~ Price+Rating+size_mb+small_app, data = df, Hess=TRUE)
summary(m)
(ctable <- coef(summary(m)))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
ctable
```



```{r}
m <- polr(ordinal~ Price, data = df, Hess=TRUE)

(ctable <- coef(summary(m)))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
ctable

summary(m)
```

```{r}
m <- polr(ordinal~ Price+Rating, data = df, Hess=TRUE)

(ctable <- coef(summary(m)))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
ctable

summary(m)
```

```{r}
m <- polr(ordinal~ Price+Rating+small_app, data = df, Hess=TRUE)
summary(m)
(ctable <- coef(summary(m)))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
ctable
```

```{r}
m <- polr(ordinal~ Price+Rating+small_app+size_mb, data = df, Hess=TRUE)
summary(m)
(ctable <- coef(summary(m)))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
ctable

```

